\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-09 coqimpl.tex
Adding information for Partial recursor.

\textit{Generating Scheme for Propositional Computation Axiom for FRecursor}. Thus we support "FScheme" to remedy problem (1): our plugin can automatically generate(postulate) the computational ``axiom'' for the specified  into the family and prove them during compilation into modules. However, it is only introducing computational information \textbf{propositionally} but not judgementally, and we might need the help of rewriting tactic on these computational ``axiom'' to justify the computation.

@@

Though partial recursor is provable by simply using "FRecursor", for convenience, we support using "FScheme" to automatic generate it. At the meantime, we implement a tactic "prec_discriminate" that when fed with the appropriate partial recursor (with computational axiom generated), it can discriminate an absurd equation between two different constructors of extensible inductive type.
\begin{minted}{Coq}
  FInductive tm : Set := tunit : tm | tvar : ident -> tm | ..
  FScheme tm_prec PRecT about self__STLC.tm.
  FScheme Rec2D about self__STLC.tm_prec.
  (* ... *)
  Goal ∀ i, tvar i = tunit -> False.
  intros i H. prec_discriminate self__STLC.tm_prec H. Qed.
\end{minted}

>>>>

\textit{Generating Scheme for Propositional Computation Axiom for FRecursor}. Thus we support "FScheme" to remedy problem (1): our plugin can automatically generate(postulate) the computational ``axiom'' for the specified  into the family and prove them during compilation into modules. For example, "FScheme Comp about subst" in \cref{fig:plugin-example2} will compile into "Module Type substtm_139", filled with all the computational axiom for "subst". There module type when included in the context can be used to reduce "subst"; they will also be proved after compilation.

However, it is only introducing computational information \textbf{propositionally} but not judgementally, and we might need the help of rewriting tactic on these computational ``axiom'' to justify the computation.

@@

Though partial recursor is provable by simply using "FRecursor", for convenience, we support using "FScheme" to automatic generate it. For example, "FScheme tm_prec PRecT" in \cref{fig:plugin-example2} can lead to compilation of "Module tm_prec_72". At the meantime, we implement a tactic "prec_discriminate" that when fed with the appropriate partial recursor (with computational axiom generated), it can discriminate an absurd equation between two different constructors of extensible inductive type.
\begin{minted}{Coq}
  FInductive tm : Set := tunit : tm | tvar : ident -> tm | ..
  FScheme tm_prec PRecT about self__STLC.tm.
  FScheme Rec2D about self__STLC.tm_prec.
  (* ... *)
  Goal ∀ i, tvar i = tunit -> False.
  intros i H. prec_discriminate self__STLC.tm_prec H. Qed.
\end{minted}
